Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2019-01-15 notes-duality/bo-notes.tex
thinking on paper. bo@nyc

  As above, if $d$-embeddable then for each level set and associated embedding point $r$, there is a set of $d$ polytopes $\{\partial \ell_y(r)\}_{y=1}^d$ such that $p$ is in the level set if and only if
  \[ 0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) . \]
  Let
    \[ H_y(v) = \max_{w \in \partial \ell_y(r)} \langle v , w \rangle . \]
  So $w \in \partial \ell(r;p)$ if and only if, for all $v$,
    \[ \langle v, w\rangle \leq \sum_y p_y H_y(v) . \]
  In particular, $p$ is in the level set if and only if, for all $v$,
    \[ 0 \leq \sum_y p_y H_y(v) . \]
  If we relax this constraint to only hold for a finite set of $v$, what happens?
\end{proof}

>>>>

  As above, if $d$-embeddable then for each level set and associated embedding point $r$, there is a set of $d$ polytopes $\{\partial \ell_y(r)\}_{y=1}^d$ such that $p$ is in the level set if and only if
  \[ 0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) . \]
  Let
    \[ H_y(v) = \max_{w \in \partial \ell_y(r)} \langle v , w \rangle . \]
  So $w \in \partial \ell(r;p)$ if and only if, for all $v$,
    \[ \langle v, w\rangle \leq \sum_y p_y H_y(v) . \]
  In particular, $p$ is in the level set if and only if, for all $v$,
    \[ 0 \leq \sum_y p_y H_y(v) . \]
  Which we know equals the set $p$ such that for $j=1,\dots,k$,
    \[ 0 \leq \sum_y p_y B_{jy} . \]
  So there are $k$ unit normals $v_1 \dots v_k$ with $H_y(v_k) = B_{jy}$.
  So the $y$th polytope is contained in something,
    \[ \partial \ell_y(r) \subseteq \{ w : Vw \leq B_y \} . \]
\end{proof}

Raf: need more than nonempty. The pentago would have a little nonempty triangle, but it wouldn't contain a maximizer from each face.

Call it a $d$-rep if the support function equals $\{p : Bp \geq 0\}$.

Pentagon
